\section{Introduction}\label{intro}

\subsection{Purpose}
With the higher focus on the impact of our urban and suburban travel on the environment and the higher accessibility of electric mobility, an increase of circulating electric vehicles can be observed.\footnote{\url{https://www.eea.europa.eu/ims/new-registrations-of-electric-vehicles}} \footnote{\url{https://www.statista.com/statistics/1101415/number-of-electric-vehicles-by-type/}} \footnote{\href{https://www.eib.org/en/surveys/climate-survey/4th-climate-survey/hybrid-electric-petrol-cars-flying-holidays-climate.htm}{European Investment Bank Climate Survey}}
This increase concerns both private vehicles and goods transporting ones.
As a result of restrictions on fuel vehicle production and sell that will concern a large part of the world's population\footnote{\href{https://en.wikipedia.org/wiki/Phase-out\_of\_fossil\_fuel\_vehicles\#Places\_with\_planned\_fossil-fuel\_vehicle\_restrictions}{Places with planned fossil-fuel vehicle restrictions}}, the number of
electric vehicle is set to increase. For these reasons, the main vehicle manufacturers have started making huge investments in electric mobility\footnote{\href{https://en.wikipedia.org/wiki/Electric\_car\#EV\_plans\_from\_major\_manufacturers}{EV plans from major manufacturers}}, which will lead to greater accessibility to the market by drivers.
\hfill \break

A main problem of electric vehicle is that a full charge requires much more time than a fuel vehicle.\footnote{\href{https://blinkcharging.com/fact-from-fiction-the-real-reason-why-consumers-dont-buy-electric-vehicles/?locale=en}{Why consumers don't buy electric vehicles}}
Thus, a single charge can have a huge impact on our daily schedule, and it is necessary to plan wisely when and where to charge.
To solve this problem is one of the main objective of the eMall - e-Mobility for All system.
\hfill \break

The following document is the RASD for the eMall - e-Mobility for All system. It provides
a description of the system focusing on the requirements and specifications, providing scenarios and use cases
to specify what the system must do, how it will interact with the stakeholders and the constraints it is subject to.

\subsubsection*{Goal}
\begin{table}[h]
    \begin{tabular}{|l|l|}
        \toprule
        \textbf{G1} & the first  \\ \midrule
        \textbf{G2} & the second \\ \midrule
                    &            \\ \bottomrule
    \end{tabular}
\end{table}

\subsection{Scope}
Here the scope introduction (a description of the context, the stakeholder ecc.)
Identifies the product and application domain
\subsubsection*{World phenomena}
\begin{table}[h]
    \begin{tabular}{|l|l|}
        \toprule
        \textbf{WP1} & the first  \\ \midrule
        \textbf{WP2} & the second \\ \midrule
                     &            \\ \bottomrule
    \end{tabular}
\end{table}
\subsubsection*{Shared phenomena}
\begin{table}[h]
    \begin{tabular}{|l|l|}
        \toprule
        \textbf{SP1} & the first  \\ \midrule
        \textbf{SP2} & the second \\ \midrule
                     &            \\ \bottomrule
    \end{tabular}
\end{table}


\subsection{Definitions, Acronyms, Abbreviations}
\subsubsection*{Definitions}
A list of definitions (if present)
\begin{itemize}
    \item 1
\end{itemize}
\subsubsection*{Acronyms}
A list of definition (if present)
\begin{itemize}
    \item 1
\end{itemize}
\subsubsection*{Abbreviation}
\begin{table}[h]
    \begin{tabular}{|l|l|}
        \toprule
        \textbf{RASD} & Requirement Analysis and Specification Document \\ \midrule
        \textbf{WP}   & World Phenomena                                 \\ \midrule
        \textbf{SP}   & Shared Phenomena                                \\ \midrule
        \textbf{G}    & Goal                                            \\ \midrule
        \textbf{D}    & Domain                                          \\ \midrule
                      &                                                 \\ \bottomrule
    \end{tabular}
\end{table}
\subsection{Revision history}
Nothing here

\subsection{Reference Documents}
Nothing here

\subsection{Document Structure}
Nothing here
